---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rbrcutils

<!-- badges: start -->
<!-- badges: end -->

The goal of rbrcutils is to provide access to functions used commonly in developing reports for the Rosemary Bryant AO Research Centre.

## Installation

You can install the development version of rbrcutils from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("darchlp/rbrcutils")
```

## Example

Currently, this package provides functionality for producing plots to visualise categorical variables (in the form of column plots) and numerical variables (in the form of box and whisker plots). These plots can either be a series of variables over the whole dataset `consecutive_**_plot` or a single variable by a grouping variable `**_group_plot`.

### Categorical variables
Plot a series of categorical variables over the whole data.
```{r consecutive_cat_plot}
library(rbrcutils)
df <- data.frame(
  "apples" = sample(
    forcats::as_factor(c("Good", "Neutral", "Bad")),
    size = 50,
    replace = T
  ),
  "bananas" = sample(
    forcats::as_factor(c("Good", "Neutral", "Bad")),
    size = 50,
    replace = T
  ),
  "pears" = sample(
    forcats::as_factor(c("Good", "Neutral", "Bad")),
    size = 50,
    replace = T
  )
)
consecutive_cat_plot(
  df,
  c("Apples" = "apples", "Bananas" = "bananas", "Pears" = "pears"),
  colors = c(
    "Bad" = "#b44218",
    "Neutral" = "#b4b4b4",
    "Good" = "#179dab"
  )
)
```

Or a categorical variable by a grouping variable.
```{r cat_group_plot}
library(rbrcutils)
df <- data.frame(
  "apples" = sample(
    forcats::as_factor(c("Good", "Neutral", "Bad")),
    size = 50,
    replace = TRUE
  ),
  "group" = sample(
    forcats::as_factor(c("Group 1", "Group 2", "Group 3")),
    size = 50,
    replace = TRUE
  )
)
cat_group_plot(
  df,
  xvar = "apples",
  yvar = "group",
  colors = c(
    "Bad" = "#b44218",
    "Neutral" = "#b4b4b4",
    "Good" = "#179dab"
  )
)
```

### Numeric variable plot
Plot a series of numerical variables over the whole data.
```{r consecutive_box_plot}
library(rbrcutils)
df <- data.frame(
  "number1" = sample(1:5, size = 50, replace = T),
  "number2" = sample(1:5, size = 50, replace = T),
  "number3" = sample(1:5, size = 50, replace = T)
)
consecutive_box_plot(
  df,
  var = c(
    "Number 1" = "number1",
    "Number 2" = "number2",
    "Number 3" = "number3"
  ),
  labels = c(
    "1" = "Strongly diagree",
    "2" = "Disagree",
    "3" = "Neutral",
    "4" = "Agree",
    "5" = "Strongly agree"
  ),
  ordered_mean = T
)
```

Or a numeric variable by a grouping variable.
```{r box_group_plot}
library(rbrcutils)
df <- data.frame(
  "number" = sample(1:5, size = 50, replace = TRUE),
  "group" = sample(
    forcats::as_factor(c("Group 1", "Group 2", "Group 3")),
    size = 50,
    replace = TRUE
  )
)

box_group_plot(
  df,
  xvar = "number",
  xvar_name = "Numeric",
  yvar = "group",
  yvar_name = "Grouping",
  labels = c(
    "1" = "Strongly disagree",
    "2" = "Disagree",
    "3" = "Neutral",
    "4" = "Agree",
    "5" = "Strongly agree"
  )
)
```